\documentclass{article}
\usepackage[utf8]{inputenc}


\author{Lukesh Patil (14451)\\ Dhekane Eeshan Gunesh (13248)\\ Hariom Panthi (150263)\\ Mandal Swarnadeep (150754)\\CS251A, Assignment 10, Prof. Arnab Bhattacharya}
\title{Reviews of Movies-- Munnabhai MBBS, 3 Idiots}
\date{\today}

\begin{document}
\maketitle

\section{Munna Bhai MBBS}
The story line of this movie revolves around Munna Bhai (played by Sanjay Dutt) and his sidekick Circuit (played by Arshad Warsi). Munna Bhai, whose real name is Murli Prasad Sharma, becomes a bhai after coming to Mumbai. His father (played by Sunil Dutt) wants him to become a doctor. Every time his father visits him in the city, his dhobi-ghaat place has to be transformed into a hospital to show that he is a real doctor. \\ 
But once Munna Bhai's father finds out the reality, he is heart-broken and leaves. This incident pushes Munna Bhai to prove a point and he gets himself an admission to become a doctor to show his worth to his father. He doesn't get along well with the dean of the college, furthermore he is also in love with his daughter (played by Gracy Singh). \\ 
The story focuses on how people in the hospital need to be loved and appreciated. Arshad Warsi provides his dose of humour after every few scenes. Songs weren't that great except perhaps a couple of them. \\ 
Sanjay Dutt does justification to his role as the Bhai. Arshad Warsi in the supporting role also acted very well. All in all, this is a very good movie if a good dose of laughter is what one is looking for.

\section{3 Idiots}
3 Idiots is the perfect end to an exciting year for India: the year when the aam aadmi voted in progress, liberalism, secularism and turned his back to corruption, communalism, regionalism. The three idiots, Rancchoddas Shyamaldas Chanchad (Aamir Khan), Raju Rastogi (Sharman Joshi) and Farhan Qureshi (R Madhavan), are perfect representatives of the new age Indian students who are non-conformist, questioning givens. They choose to live their lives on their own terms. But due to societal and parental pressure they are forced to have educational paths that they refuse to chose so that they do not become cogs in the wheel. Naturally, they end up as great successes who shaped the world by taking the roads less travelled.\\
The film begins with the entry of the trio in the city's elite engineering college. It takes the first tryst with the mandatory ragging sessions which decides who the leader of the gang is going to be and in the movie, it is the new entrant Baba Rancchoddas, as his friends would fondly call him. Rancho not only leads his friends through the maze of India's highly competitive, high-pressure and almost cruel educational rat-race, but also tutors them with several life mantras. Some of these matras include ``running after excellence and not success'', ``questioning and not blindly accepting the givens'', ``inventing and experimenting in lieu of copying and cramming'' and most importantly ``following your heart's calling if you truly want to make a difference''.
\\
I'm an IITian myself and hence, needless to say, was looking forward to this movie as it is based on the life in IITs. I went with my family and watched the first-day-first-show and was I pleased ? In one sentence - The best Bollywood movie ever ! If you are into movies, then this one is not to be missed unless you are the 4th idiot. I cried, I laughed and I enjoyed every moment of the 3 hours that I spent watching this gem. The songs that seemed mediocre before watching the movie, feel like perfect for the movie. They are so ideal for the situations that I just loved them.



\section{Patil's Review}

\subsection{Munna Bhai MBBS}

 Munna Bhai (Sanjay Dutt) and his gang are the typical 'Bhai's in Mumbai who claims to be a social worker helping out people in recovery (through kidnapping, haath-pair todna) etc and has lied to his father that he is a doctor. When the truth is discovered, an insulted Munna then makes a resolve to become a doctor. Coincidentally, he joins the same college where his enemy Dr. Asthana (Boman Irani) is a strict Dean. A comedy of troubles starts when the 'cool' don confronts strict Asthana.

\subsection{3 idiots}

As you can understand, they could not bring the name of any IIT into the movie to avoid disputes. But trust me, whatever they have shown about the life in IITs, it's all true. Right from suicides, cold-hearted Professors to lack of encouragement and support for talents who can really bring serious change in this world. The movie successfully depicts how once inside, your life is only about meaningless grades, go get into the race before it's too late.

\section{Eeshan's Review}
\subsection{Munna Bhai MBBS}
In my opinion, the movie Munnabhai MBBS show many important characteristics of ethical and social importance. It shows that hard-work and honesty always succeeds. It also shows that any wrong deeds can always be forgiven once we decide to admit them and act upon them. The acting of Sanjay Dutt and Arshad Warsi is phenomenal. I would like to give this movie 3 stars out of 5. The songs of the movie are also catchy. Overall it has been a hit on box-office and it is definitely worth the time! 
\subsection{3 Idiots}
To speak about 3 Idiots, it is an extremely good and a must-watch movie. It portrays the current situtation of many Indian students who are forced into academic fields without a definitive interest. The movie shows in a very humorous way some of the deep problems in our educational and social structure. But it also gives out many good messages to students, most important of which is `never give up on your dreams and never give up your efforts! Thumbs up and hats off to the songs, the overall cinematography and the movie! 4.5 stars out of 5 from my side!'

\section{Swarnadeep's Review}
\subsection{Munna Bhai MBBS}
The movie Munna Bhai M.B.B.S. is an exemplary example of how a humerous movie can be made. The movie is filled with jokes and comical scenes every second minute. There are instances when the mood of the movie changes from the humerous one to a serious one. And such changes are more than welcome as the audience goes through a lot of emotions. The character development of the lead characters is tremendous. The audience, by the end of the movie, starts to resonate with the feelings of both the lead actors and thus the movie ends with the audience having happy faces and wondering how quickly the 2.5 hours went by. This movie is a must watch for all people who are looking forward to a jovial session of movie watching. 10/10 would recomment. 
\subsection{3 Idiots}
The movie 3 idiots show some major life lessons in ways that the audience not only enjoys, but also relates to. There are a lot of humerous elements to the story too. The story revolves around a group of 3 college students, their hardships, their struggles and their journey to become successful in their respective fields. The fact that the movie not only showcases the ups of the college life but also the downs, like the scene when Raju attempts suicide, makes this movie a great one. While watching the movie, one goes through a plethora of emotions, ranging from sorrow, grief to joy and happiness. The movie also focuses on the rat race that our education system is. This movie is a must watch for all college students and everyone who thinks he/she is stuck in their life and are not going forward. 10/10 would recommend.

\section{Hariom's review}
\subsection{Munna Bhai MBBS}
Inspired by the Hollywood movie 'Patch Adam', 'Munnabhai M.B.B.S.' tells the comedic story of a thug who wants to become a doctor. The film has its major share of comedic moments and its dramatic moments. It is indeed an entertaining film with the famously lovable characters like Munnabhai and Circuit. 
\\
Rajkumar Hirani may have taken the idea of an older outsider wanting to become a doctor from 'Patch Adams' but in essence 'Munnabhai M.B.B.S.' is its own film and it is the performances and comedy that make it worth the watch because most the dramatic moments are a little over the top. While the dialogue in the comedic scenes are witty and hilarious, the ones in the dramatic scenes are a mess.
\\
Sanjay Dutt totally nails Munnabhai. It's hard to picture anyone else in the title role. The actor does full justice. It was nice to see Sunil Dutt after a long time and that too as father to his own son. The actor has a strong presence, even in a brief role. Gracy Singh is cute and adorable. Jimmy Shergill is awesome and holds his own as Zaheer and Boman Irani too does very well. However, it is Arshad Warsi who steals the show in a breakthrough performance as one of the most memorable film characters of recent time, Circuit.
\\
Most of the songs are well balanced and are good additions to the film. I found Munnabhai's romantic ballad hilarious when he tries to convince the suicider to cut the crap. On the technical side, it's alright. On the whole this is one enjoyable flick.
\subsection{3 Idiots}
The movie has many hilarious scenes and everyone in the film form Aamir to Boman Irani to Omi Vaidya were superb in their roles.. Aamir has outdone himself.. Never in the film he has looked 44 year old... Film's music sounds mediocre but when viewed on the screen then the music sounds perfect.. Cinematography is awesome and so is the direction.. Raju Hirani's screenplay(you can easily ignore a few loose points) is a masterpiece and the film will achieve cult status for engineering students in a short period of time.. It has the soul which Five Point Someone had.. It is easily Aamir Khan's finest film to date.. The film's climax is fantabulous and is a shocker.. It takes everyone by surprise...



\end{document}

